Data Management \\ and LSST Special Programs

### 2021-11-27 DMTN-065.tex
added reference to RTN-008 (GW use-case)

\setDocChangeRecord{%
\addtohist{0}{2017-11-14}{Status: internal working document.}{Melissa Graham}
\addtohist{1}{2018-06-17}{Updated to finalize and issue.}{Melissa Graham}
\addtohist{2}{2021-12-01}{Updated per DM-20375.}{Melissa Graham}
}

@@

\textbf{Shorter Exposures.} The camera constraint on the minimum supported exposure time is currently 1 second (stretch goal 0.1 seconds; LSR-REQ-0111 in \citeds{LSE-29}).
As with all requirements, this one would be verified during commissioning.
Assuming that 1 second exposure can be reduced and calibrated, its detected point sources will span a dynamic range of $r \approx 12.9$ -- $21.0$ magnitudes.
A template image built on $15$ second exposures will saturate at $r \approx 15.8$, but this still leaves stars between $15.8$--$21.0$ magnitudes to be used in the PSF-matching (and all other filters have a similarly large overlap).
However, in order for an image to be successfully PSF-matched to the template, the PSF must be well formed (no speckle pattern), and have a spatial variance that the pipeline is capable of modeling (be smoothly varying on some minimal scale).
As a simple demonstration, Figure \ref{fig:expt} shows that perhaps exposure times shorter than $2$ seconds do not have a well-formed PSF (using the centroid of a 2D Gaussian fit as a proxy for "well-formed").

@@

>>>>

\setDocChangeRecord{%
\addtohist{0}{2017-11-14}{Status: internal working document.}{Melissa Graham}
\addtohist{1}{2018-06-17}{Updated to finalize and issue.}{Melissa Graham}
\addtohist{2}{2021-12-01}{Minor updates as per DM-20375.}{Melissa Graham}
}

@@

\textbf{Shorter Exposures.}
The LSST System Requirements document states that {\it ``The LSST shall be capable of obtaining and processing exposures not taken in a standard visit mode including those with a minimum exposure time of} {\tt minExpTime}", which is 1 second (stretch goal 0.1 seconds; LSR-REQ-0111 in \citeds{LSE-29}).
As with all requirements, this one would be verified during commissioning.
Assuming that 1 second exposure can be reduced and calibrated, its detected point sources will span a dynamic range of $r \approx 12.9$ -- $21.0$ magnitudes.
A template image built on $15$ second exposures will saturate at $r \approx 15.8$, but this still leaves stars between $15.8$--$21.0$ magnitudes to be used in the PSF-matching (and all other filters have a similarly large overlap).
However, in order for an image to be successfully PSF-matched to the template, the PSF must be well formed (no speckle pattern), and have a spatial variance that the pipeline is capable of modeling (be smoothly varying on some minimal scale).
As a simple demonstration, Figure \ref{fig:expt} shows that perhaps exposure times shorter than $2$ seconds do not have a well-formed PSF (using the centroid of a 2D Gaussian fit as a proxy for "well-formed").

@@

% % % % % % %
\subsection{Gravitational Wave Event Follow-Up}\label{ssec:SPCS_GW}

For a description of how target of opportunity data to search for the optical counterparts of gravitational wave events would be processed, sen \citeds{rtn-008}.
